NUll check for flashr2

### 2017-09-17 analysis/nullcheck2.Rmd
Files commited by wflow_commit.

---
title: "null check for flashr2"
author: "wei"
date: 09-16
output: html_document
---

@@

set.seed(99)
T = 1000
lambda_0 = rep(NA,T)
flash_rank_0= rep(1,T)
flash2_rank_0= rep(1,T)
for(t in 1:T){
  P = 300
  N = 100
  Sigma_0 = diag(rep(1,P))
  X = mvrnorm(n = N,mu = rep(0,P), Sigma = Sigma_0)
  lambda_0[t] =  svd(X)$d[1]
  data = set_flash_data(X)
  g1= flash_r1(data,verbose=F)
  g2 = flashr::flash(X)
  if(sum(g1$EL) ==0 )  {flash2_rank_0[t] = 0}
  if(sum(g2$l) ==0 )  {flash_rank_0[t] = 0}
}

set.seed(99)
T = 1000
lambda_1 = rep(NA,T)
flash_rank_1= rep(1,T)
flash2_rank_1= rep(1,T)
for(t in 1:T){
  P = 300
  N = 100
  Sigma_0 = diag(rep(1,P))
  nu = rnorm(P, 0, (6)/(sqrt(P)))
  index_nu = sample(seq(1:P),(P*0.95))
  nu[index_nu] = 0
  Sigma_1 = Sigma_0 + nu %*% t(nu)
  X = mvrnorm(n = N,mu = rep(0,P), Sigma = Sigma_1)
  lambda_1[t] =  svd(X)$d[1]
  data = set_flash_data(X)
  g1= flash_r1(data,verbose=F)
  g2 = flashr::flash(X)
  if(sum(g1$EL) ==0 )  {flash2_rank_1[t] = 0}
  if(sum(g2$l) ==0 )  {flash_rank_1[t] = 0}
}

>>>>

---
title: "NUll check for flashr2"
author: "Wei Wang"
date: 09-17
output: html_document
---

@@

set.seed(99)
T = 1000
lambda_0 = rep(NA,T)
flash_rank_0= rep(1,T)
flash2_rank_0= rep(1,T)
for(t in 1:T){
  P = 300
  N = 100
  Sigma_0 = diag(rep(1,P))
  X = mvrnorm(n = N,mu = rep(0,P), Sigma = Sigma_0)
  lambda_0[t] =  svd(X)$d[1]
  data = set_flash_data(X)
  g1= flash_r1(data,verbose=F)
  g2 = flashr::flash(X,objtype = "l",
                     ash_para_l = list(nullweight = 1 ),
                     ash_para_f = list(nullweight = 1 ))
  if(sum(g1$EL) ==0 )  {flash2_rank_0[t] = 0}
  if(sum(g2$l) ==0 )  {flash_rank_0[t] = 0}
}

set.seed(99)
T = 1000
lambda_1 = rep(NA,T)
flash_rank_1= rep(1,T)
flash2_rank_1= rep(1,T)
for(t in 1:T){
  P = 300
  N = 100
  Sigma_0 = diag(rep(1,P))
  nu = rnorm(P, 0, (1)/(sqrt(P)))
  # index_nu = sample(seq(1:P),(P*0.95))
  # nu[index_nu] = 0
  Sigma_1 = Sigma_0 + nu %*% t(nu)
  X = mvrnorm(n = N,mu = rep(0,P), Sigma = Sigma_1)
  lambda_1[t] =  svd(X)$d[1]
  data = set_flash_data(X)
  g1= flash_r1(data,verbose=F)
  g2 = flashr::flash(X,objtype = "l",
                     ash_para_l = list(nullweight = 1 ),
                     ash_para_f = list(nullweight = 1 ))
  if(sum(g1$EL) ==0 )  {flash2_rank_1[t] = 0}
  if(sum(g2$l) ==0 )  {flash_rank_1[t] = 0}
}
